A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-08 paper.tex
edits in related work

\todo[inline]{KC: [IMPORTANT] KC, please add \url{https://arxiv.org/abs/2001.11560}
to this section.}

We review closely related work in three areas: coercions in normal
form, threesomes, and parameterized cast calculi.

>>>>

\citet{siek2020mechanized} defines two dynamic semantics for 
cast calculi parameterized over cast representations, similar to
our \CMachine{B}. The two corresponding interfaces, namely
$\mathrm{CastStruct}$ and $\mathrm{EfficientCastStruct}$, give
users more control over the structure of values. \CMachine{B} machine
insists that the cast on the top of a value must be a function cast
or a product cast. In contrast, users of their interfaces define
a predicate on casts called $\mathrm{Inert}$ and any inert cast can
be a part of a value. Their system doesn't include theorems relating
space-inefficient cast calculi and space-efficient ones, which
is one of the major goals of our framework.

% We review closely related work in three areas: coercions in normal
% form, threesomes, and parameterized cast calculi.
